---
title: "Homework #2: Point Interpolation"
author: Haley Chinander
output:
  flexdashboard::flex_dashboard:
    navbar:
      - { icon: "fa-github", href: "https://github.com/SpatialDataAssignments/SDA_Homework2", align: right }
---

```{r setup, include=FALSE}
library(flexdashboard) 

#Map
mapLink='https://github.com/SpatialDataAssignments/SDA_Homework2/raw/refs/heads/main/plot1.rds'

map=url(mapLink)

#Table

tablelink='https://github.com/SpatialDataAssignments/SDA_Homework2/raw/refs/heads/main/table.rds'

table=url(tablelink)


```

## Sidebar {.sidebar}

**Task:** Determine the appropriate nightly rate to charge for a home rental on AirBNB using point interpolation. This code interpolated the prices from AirBnbs with similar characteristics to any other location in between.

**Interpolation approach:** Inverse Distance Weighting, using 10 closest units.

**Estate address:** 20 Maynard Pl, Cambridge, MA 02138

**Characteristics**: The rental is an entire home with 3 bedrooms and 3 baths.

## Column {.tabset .tabset-fade}

### Point Interpolation Map:

```{r}

readRDS(map)

```

### Table of difference point interpolation approaches:

```{r}
readRDS(table)
```
